\item[\textbf{A1.}]Let $n \geq 2$ be a fixed integer. Find the least constant $C$ such the inequality\[\sum_{i<j} x_{i}x_{j} \left(x^{2}_{i}+x^{2}_{j} \right) \leq C
\left(\sum_{i}x_{i} \right)^4\]

holds for any $x_{1}, \ldots ,x_{n} \geq 0$ (the sum on the left consists of $\binom{n}{2}$ summands). For this constant $C$,  characterize the instances of equality.

\item[\textbf{A2.}]The numbers from 1 to $n^2$  are randomly arranged in the cells of a $n \times n$ square ($n \geq 2$). For any pair of numbers situated on the same row or on the same column the ratio of the greater number to the smaller number is calculated.  Let us call the characteristic of the arrangement the smallest of these $n^2\left(n-1\right)$ fractions. What is the highest possible value of the characteristic ?

\item[\textbf{A3.}]A game is played by $n$ girls ($n \geq 2$), everybody having a ball. Each of the $\binom{n}{2}$ pairs of players, is an arbitrary order, exchange the balls they have at the moment. The game is called nice nice if at the end nobody has her own ball and it is called tiresome if at the end everybody has her initial ball. Determine the values of $n$ for which there exists a nice game and those for which there exists a tiresome game.

\item[\textbf{A4.}]Prove that the set of positive integers cannot be partitioned into three nonempty subsets such that, for any two integers $x,y$ taken from two different subsets, the number $x^2-xy+y^2$ belongs to the third subset.

\item[\textbf{A5.}]Find all the functions $f: \mathbb{R} \to\mathbb{R}$ such that\[f(x-f(y))=f(f(y))+xf(y)+f(x)-1\]for all $x,y \in \mathbb{R} $.

\item[\textbf{A6.}]For $n \geq 3$ and $a_{1} \leq a_{2} \leq \ldots \leq a_{n}$ given real numbers we have the following instructions:

\begin{itemize}

\item place out the numbers in some order in a ring;

\item delete one of the numbers from the ring;

\item if just two numbers are remaining in the ring: let $S$ be the sum of these two numbers. Otherwise, if there are more the two numbers in the ring, replace

\end{itemize}

Afterwards start again with the step (2). Show that the largest sum $S$ which can result in this way is given by the formula\[S_{max}= \sum^n_{k=2} \begin{pmatrix} n -2 \\

[\frac{k}{2}] - 1\end{pmatrix}a_{k}.\]

