\item[\textbf{C1.}]Let $n \geq 1$ be an integer. A path from $(0,0)$ to $(n,n)$ in the $xy$ plane is a chain of consecutive unit moves either to the right (move denoted by $E$) or upwards (move denoted by $N$), all the moves being made inside the half-plane $x \geq y$. A step in a path is the occurence of two consecutive moves of the form $EN$. Show that the number of paths from $(0,0)$ to $(n,n)$ that contain exactly $s$ steps $(n \geq s \geq 1)$ is\[\frac{1}{s} \binom{n-1}{s-1} \binom{n}{s-1}.\]

\item[\textbf{C2.}]If a $5 \times n$ rectangle can be tiled using $n$ pieces like those shown in the diagram, prove that $n$ is even. Show that there are more than $2 \cdot 3^{k-1}$ ways to file a fixed $5 \times 2k$ rectangle $(k \geq 3)$ with $2k$ pieces. (Symmetric constructions are supposed to be different.)

\item[\textbf{C3.}]A biologist watches a chameleon. The chameleon catches flies and rests after each catch. The biologist notices that:

\begin{itemize}

\item the first fly is caught after a resting period of one minute;

\item the resting period before catching the $2m^\text{th}$ fly is the same as the resting period before catching the $m^\text{th}$ fly and one minute shorter than the resting period before catching the $(2m+1)^\text{th}$ fly;

\item when the chameleon stops resting, he catches a fly instantly.

\end{itemize}

How many flies were caught by the chameleon before his first resting period of $9$ minutes in a row? After how many minutes will the chameleon catch his $98^\text{th}$ fly? How many flies were caught by the chameleon after 1999 minutes have passed?

\item[\textbf{C4.}]Let $A$ be a set of $N$ residues $\pmod{N^{2}}$. Prove that there exists a set $B$ of of $N$ residues $\pmod{N^{2}}$ such that $A + B = \{a+b\ |\ a \in A, b \in B\}$ contains at least half of all the residues $\pmod{N^{2}}$.

\item[\textbf{C5.}]Let $n$ be an even positive integer. We say that two different cells of a $n \times n$ board are neighboring if they have a common side. Find the minimal number of cells on the $n \times n$ board that must be marked so that any cell (marked or not marked) has a marked neighboring cell.

\item[\textbf{C6.}]Suppose that every integer has been given one of the colours red, blue, green or yellow. Let $x$ and $y$ be odd integers so that $|x| \neq |y|$. Show that there are two integers of the same colour whose difference has one of the following values: $x,y,x+y$ or $x-y$.

\item[\textbf{C7.}]Let $p >3$ be a prime number. For each nonempty subset $T$ of $\{0,1,2,3, \ldots , p-1\}$,  let $E(T)$ be the set of all $(p-1)$-tuples $(x_1, \ldots ,x_{p-1} )$,  where each $x_i \in T$ and $x_1+2x_2+ \ldots + (p-1)x_{p-1}$ is divisible by $p$ and let $|E(T)|$ denote the number of elements in $E(T)$. Prove that\[|E(\{0,1,3\})| \geq |E(\{0,1,2\})|\]

with equality if and only if $p = 5$.