\item[\textbf{G1.}]In the plane we are given two circles intersecting at $ X$ and $ Y$. Prove that there exist four points with the following property:

(P) For every circle touching the two given circles at $ A$ and $ B$,  and meeting the line $ XY$ at $ C$ and $ D$,  each of the lines $ AC$,  $ AD$,  $ BC$,  $ BD$ passes through one of these points.

\item[\textbf{G2.}]Two circles $ G_1$ and $ G_2$ intersect at two points $ M$ and $ N$. Let $ AB$ be the line tangent to these circles at $ A$ and $ B$,  respectively, so that $ M$ lies closer to $ AB$ than $ N$. Let $ CD$ be the line parallel to $ AB$ and passing through the point $ M$,  with $ C$ on $ G_1$ and $ D$ on $ G_2$. Lines $ AC$ and $ BD$ meet at $ E$; lines $ AN$ and $ CD$ meet at $ P$; lines $ BN$ and $ CD$ meet at $ Q$. Show that $ EP = EQ$.

\item[\textbf{G3.}]Let $O$ be the circumcenter and $H$ the orthocenter of an acute triangle $ABC$.  Show that there exist points $D$,  $E$,  and $F$ on sides $BC$,  $CA$,  and $AB$ respectively such that \[ OD + DH = OE + EH = OF + FH\] and the lines $AD$,  $BE$,  and $CF$ are concurrent.

\item[\textbf{G4.}]Let $ A_1A_2 \ldots A_n$ be a convex polygon, $ n \geq 4.$ Prove that $ A_1A_2 \ldots A_n$ is cyclic if and only if to each vertex $ A_j$ one can assign a pair $ (b_j, c_j)$ of real numbers, $ j = 1, 2, \ldots, n,$ so that $ A_iA_j = b_jc_i - b_ic_j$ for all $ i, j$ with $ 1 \leq i < j \leq n.$

\item[\textbf{G5.}]The tangents at $B$ and $A$ to the circumcircle of an acute angled triangle $ABC$ meet the tangent at $C$ at $T$ and $U$ respectively.  $AT$ meets $BC$ at $P$,  and $Q$ is the midpoint of $AP$; $BU$ meets $CA$ at $R$,  and $S$ is the midpoint of $BR$.  Prove that $\angle ABQ=\angle BAS$.  Determine, in terms of ratios of side lengths, the triangles for which this angle is a maximum.

\item[\textbf{G6.}]Let $ ABCD$ be a convex quadrilateral. The perpendicular bisectors of its sides $ AB$ and $ CD$ meet at $ Y$. Denote by $ X$ a point inside the quadrilateral $ ABCD$ such that $ \measuredangle ADX = \measuredangle BCX < 90^{\circ}$ and $ \measuredangle DAX = \measuredangle CBX < 90^{\circ}$. Show that $ \measuredangle AYB = 2\cdot\measuredangle ADX$.

\item[\textbf{G7.}]Ten gangsters are standing on a flat surface, and the distances between them are all distinct. At twelve o’clock, when the church bells start chiming, each of them fatally shoots the one among the other nine gangsters who is the nearest. At least how many gangsters will be killed?

\item[\textbf{G8.}]Let $ AH_1, BH_2, CH_3$ be the altitudes of an acute angled triangle $ ABC$. Its incircle touches the sides $ BC, AC$ and $ AB$ at $ T_1, T_2$ and $ T_3$ respectively. Consider the symmetric images  of  the  lines $ H_1H_2, H_2H_3$ and $ H_3H_1$ with  respect  to  the  lines $ T_1T_2, T_2T_3$ and $ T_3T_1$.  Prove  that  these  images  form a  triangle  whose  vertices  lie  on  the incircle of $ ABC$.