\item[\textbf{C1.}]Let $n$ be a positive integer. Each point $(x,y)$ in the plane, where $x$ and $y$ are non-negative integers with $x+y<n$,  is coloured red or blue, subject to the following condition: if a point $(x,y)$ is red, then so are all points $(x',y')$ with $x'\leq x$ and $y'\leq y$. Let $A$ be the number of ways to choose $n$ blue points with distinct $x$-coordinates, and let $B$ be the number of ways to choose $n$ blue points with distinct $y$-coordinates. Prove that $A=B$.

\item[\textbf{C2.}]For $n$ an odd positive integer, the unit squares of an $n\times n$ chessboard are coloured alternately black and white, with the four corners coloured black. A it tromino is an $L$-shape formed by three connected unit squares. For which values of $n$ is it possible to cover all the black squares with non-overlapping trominos?  When it is possible, what is the minimum number of trominos needed?

\item[\textbf{C3.}]Let $n$ be a positive integer. A sequence of $n$ positive integers (not necessarily distinct) is called full if it satisfies the following condition: for each positive integer $k\geq2$,  if the number $k$ appears in the sequence then so does the number $k-1$,  and moreover the first occurrence of $k-1$ comes before the last occurrence of $k$. For each $n$,  how many full sequences are there ?

\item[\textbf{C4.}]Let $T$ be the set of ordered triples $(x,y,z)$,  where $x,y,z$ are integers with $0\leq x,y,z\leq9$. Players $A$ and $B$ play the following guessing game. Player $A$ chooses a triple $(x,y,z)$ in $T$,  and Player $B$ has to discover $A$'s triple in as few moves as possible.  A move consists of the following: $B$ gives $A$ a triple $(a,b,c)$ in $T$,  and $A$ replies by giving $B$ the number $\left|x+y-a-b\right |+\left|y+z-b-c\right|+\left|z+x-c-a\right|$. Find the minimum number of moves that $B$ needs to be sure of determining $A$'s  triple.

\item[\textbf{C5.}]Let $r\geq2$ be a fixed positive integer, and let $F$ be an infinite family of sets, each of size $r$,  no two of which are disjoint. Prove that there exists a set of size $r-1$ that meets each set in $F$.

\item[\textbf{C6.}]Let $n$ be an even positive integer. Show that there is a permutation $\left(x_{1},x_{2},\ldots,x_{n}\right)$ of $\left(1,\,2,\,\ldots,n\right)$ such that for every $i\in\left\{1,\ 2,\ ...,\ n\right\}$,  the number $x_{i+1}$ is one of the numbers $2x_{i}$,  $2x_{i}-1$,  $2x_{i}-n$,  $2x_{i}-n-1$. Hereby, we use the cyclic subscript convention, so that $x_{n+1}$ means $x_{1}$.

\item[\textbf{C7.}]Among a group of 120 people, some pairs are friends. A weak quartet is a set of four people containing exactly one pair of friends. What is the maximum possible number of weak quartets ?