\item[\textbf{C1.}]Let $A$ be a $101$-element subset of the set $S=\{1,2,\ldots,1000000\}$. Prove that there exist numbers $t_1$,  $t_2, \ldots, t_{100}$ in $S$ such that the sets  \[ A_j=\{x+t_j\mid x\in A\},\qquad j=1,2,\ldots,100  \]  are pairwise disjoint.
\item[\textbf{C2.}]Let $D_1$,  $D_2$,  ..., $D_n$ be closed discs in the plane. (A closed disc is the region limited by a circle, taken jointly with this circle.) Suppose that every point in the plane is contained in at most $2003$ discs $D_i$. Prove that there exists a disc $D_k$ which intersects at most $7\cdot 2003 - 1 = 14020$ other discs $D_i$.
\item[\textbf{C3.}]Let $n \geq 5$ be a given integer.  Determine the greatest integer $k$ for which there exists a polygon with $n$ vertices (convex or not, with non-selfintersecting boundary) having $k$ internal right angles.
\item[\textbf{C4.}]Let $x_1,\ldots, x_n$ and $y_1,\ldots, y_n$ be real numbers.  Let $A = (a_{ij})_{1\leq i,j\leq n}$ be the matrix with entries \[a_{ij} = \begin{cases}1,&\text{if }x_i + y_j\geq 0;\\0,&\text{if }x_i + y_j < 0.\end{cases}\]Suppose that $B$ is an $n\times n$ matrix with entries $0$,  $1$ such that the sum of the elements in each row and each column of $B$ is equal to the corresponding sum for the matrix $A$.  Prove that $A=B$.
\item[\textbf{C5.}]Every point with integer coordinates in the plane is the center of a disk with radius $1/1000$.

(1) Prove that there exists an equilateral triangle whose vertices lie in different discs.

(2) Prove that every equilateral triangle with vertices in different discs has side-length greater than $96$.Radu Gologan, RomaniaRemarkThe "> 96" in (b) can be strengthened to "> 124". By the way, part (a) of this problem is the place where I used the well-known "Dedekind" theorem.
\item[\textbf{C6.}]Let $f(k)$ be the number of integers $n$ satisfying the following conditions:

(i) $0\leq n < 10^k$ so $n$ has exactly $k$ digits (in decimal notation), with leading zeroes allowed;

(ii) the digits of $n$ can be permuted in such a way that they yield an integer divisible by $11$.

Prove that $f(2m) = 10f(2m-1)$ for every positive integer $m$.