\item[\textbf{C1.}]There are $10001$ students at an university. Some students join together to form several clubs (a student may belong to different clubs). Some clubs join together to form several societies (a club may belong to different societies). There are a total of $k$ societies. Suppose that the following conditions hold:i.) Each pair of students are in exactly one club.ii.) For each student and each society, the student is in exactly one club of the society.iii.) Each club has an odd number of students. In addition, a club with ${2m+1}$ students ($m$ is a positive integer) is

in exactly $m$ societies.

Find all possible values of $k$.

\item[\textbf{C2.}]Let ${n}$ and $k$ be positive integers. There are given ${n}$ circles in the plane. Every two of them intersect at two distinct points, and all points of intersection they determine are pairwise distinct (i. e. no three circles have a common point). No three circles have a point in common. Each intersection point must be colored with one of $n$ distinct colors so that each color is used at least once and exactly $k$ distinct colors occur on each circle. Find all values of $n\geq 2$ and $k$ for which such a coloring is possible.

\item[\textbf{C3.}]The following operation is allowed on a finite graph: Choose an arbitrary cycle of length 4 (if there is any), choose an arbitrary edge in that cycle, and delete it from the graph. For a fixed integer ${n\ge 4}$,  find the least number of edges of a graph that can be obtained by repeated applications of this operation from the complete graph on $n$ vertices (where each pair of vertices are joined by an edge).

\item[\textbf{C4.}]Consider a matrix of size $n\times n$ whose entries are real numbers of absolute value not exceeding $1$. The sum of all entries of the matrix is $0$. Let $n$ be an even positive integer. Determine the least number $C$ such that every such matrix necessarily has a row or a column with the sum of its entries not exceeding $C$ in absolute value.

\item[\textbf{C5.}]$A$ and $B$ play a game, given an integer $N$,  $A$ writes down $1$ first, then every player sees the last number written and if it is $n$ then in his turn he writes $n+1$ or $2n$,  but his number cannot be bigger than $N$. The player who writes $N$ wins. For which values of $N$ does $B$ win?

\item[\textbf{C6.}]For an ${n\times n}$ matrix $A$,  let $X_{i}$ be the set of entries in row $i$,  and $Y_{j}$ the set of entries in column $j$,  ${1\leq i,j\leq n}$. We say that $A$ is golden if ${X_{1},\dots ,X_{n},Y_{1},\dots ,Y_{n}}$ are distinct sets. Find the least integer $n$ such that there exists a ${2004\times 2004}$ golden matrix with entries in the set ${\{1,2,\dots ,n\}}$.

\item[\textbf{C7.}]Define a "hook" to be a figure made up of six unit squares as shown below in the picture, or any of the figures obtained by applying rotations and reflections to this figure.

\begin{tikzpicture}
unitsize(0.5 cm);
draw((0,0)--(1,0));
draw((0,1)--(1,1));
draw((2,1)--(3,1));
draw((0,2)--(3,2));
draw((0,3)--(3,3));
draw((0,0)--(0,3));
draw((1,0)--(1,3));
draw((2,1)--(2,3));
draw((3,1)--(3,3));
\end{tikzpicture}

Determine all $ m\times n$ rectangles that can  be covered without gaps and without overlaps with hooks such that

- the rectangle is covered without gaps and without overlaps

- no part of a hook covers area outside the rectangle.

\item[\textbf{C8.}]For a finite graph $G$,  let $f(G)$ be the number of triangles and $g(G)$ the number of tetrahedra formed by edges of $G$. Find the least constant $c$ such that \[g(G)^3\le c\cdot f(G)^4\] for every graph $G$.