\item[\textbf{G1.}]
Let 
$ABC$
 be triangle with incenter 
$I$.
 A point 
$P$
 in the interior of the triangle satisfies 
\[\angle PBA+\angle PCA = \angle PBC+\angle PCB.\]
 Show that 
$AP \geq AI$, 
 and that equality holds if and only if 
$P=I$.

\item[\textbf{G2.}]
Let 
$ ABC$
 be a trapezoid with parallel sides 
$ AB > CD$.
 Points 
$ K$
 and 
$ L$
 lie on the line segments 
$ AB$
 and 
$ CD$, 
 respectively, so that 
$AK/KB=DL/LC$.
 Suppose that there are points 
$ P$
 and 
$ Q$
 on the line segment 
$ KL$
 satisfying 
\[\angle{APB} = \angle{BCD}\qquad\text{and}\qquad \angle{CQD} = \angle{ABC}.\]
 Prove that the points 
$ P$, 
$ Q$, 
$ B$
 and 
$ C$
 are concyclic.

\item[\textbf{G3.}]
Let 
$ ABCDE$
 be a convex pentagon such that
\[ \angle BAC = \angle CAD = \angle DAE\qquad \text{and}\qquad \angle ABC = \angle ACD = \angle ADE.
\]
The diagonals 
$BD$
 and 
$CE$
 meet at 
$P$.
  Prove that the line 
$AP$
 bisects the side 
$CD$.

\item[\textbf{G4.}]
A point 
$D$
 is chosen on the side 
$AC$
 of a triangle 
$ABC$
 with 
$\angle C < \angle A < 90^\circ$
 in such a way that 
$BD=BA$.
  The incircle of 
$ABC$
 is tangent to 
$AB$
 and 
$AC$
 at points 
$K$
 and 
$L$, 
 respectively.  Let 
$J$
 be the incenter of triangle 
$BCD$.
  Prove that the line 
$KL$
 intersects the line segment 
$AJ$
 at its midpoint.

\item[\textbf{G5.}]
In triangle 
$ABC$, 
 let 
$J$
 be the center of the excircle tangent to side 
$BC$
 at 
$A_{1}$
 and to the extensions of the sides 
$AC$
 and 
$AB$
 at 
$B_{1}$
 and 
$C_{1}$
 respectively. Suppose that the lines 
$A_{1}B_{1}$
 and 
$AB$
 are perpendicular and intersect at 
$D$.
 Let 
$E$
 be the foot of the perpendicular from 
$C_{1}$
 to line 
$DJ$.
 Determine the angles 
$\angle{BEA_{1}}$
 and 
$\angle{AEB_{1}}$.

\item[\textbf{G6.}]
Circles 
$ w_{1}$
 and 
$ w_{2}$
 with centres 
$ O_{1}$
 and 
$ O_{2}$
 are externally tangent at point 
$ D$
 and internally tangent to a circle 
$ w$
 at points 
$ E$
 and 
$ F$
 respectively. Line 
$ t$
 is the common tangent of 
$ w_{1}$
 and 
$ w_{2}$
 at 
$ D$.
 Let 
$ AB$
 be the diameter of 
$ w$
 perpendicular to 
$ t$, 
 so that 
$ A, E, O_{1}$
 are on the same side of 
$ t$.
 Prove that lines 
$ AO_{1}$, 
$ BO_{2}$, 
$ EF$
 and 
$ t$
 are concurrent.

\item[\textbf{G7.}]
In a triangle 
$ ABC$, 
 let 
$ M_{a}$, 
$ M_{b}$, 
$ M_{c}$
 be the midpoints of the sides 
$ BC$, 
$ CA$, 
$ AB$,  respectively, and 
$ T_{a}$, 
$ T_{b}$, 
$ T_{c}$
 be the midpoints of the arcs 
$ BC$, 
$ CA$, 
$ AB$
 of the circumcircle of 
$ ABC$, 
 not containing the vertices 
$ A$, 
$ B$, 
$ C$, 
 respectively. For 
$ i \in \left\{a, b, c\right\}$, 
 let 
$ w_{i}$
 be the circle with 
$ M_{i}T_{i}$
 as diameter. Let 
$ p_{i}$
 be the common external common tangent to the circles 
$ w_{j}$
 and 
$ w_{k}$
 (for all 
$ \left\{i, j, k\right\}= \left\{a, b, c\right\}$)
 such that 
$ w_{i}$
 lies on the opposite side of 
$ p_{i}$
 than 
$ w_{j}$
 and 
$ w_{k}$
 do.


Prove that the lines 
$ p_{a}$, 
$ p_{b}$, 
$ p_{c}$
 form a triangle similar to 
$ ABC$
 and find the ratio of similitude.

\item[\textbf{G8.}]
Let 
$ABCD$
 be a convex quadrilateral. A circle passing through the points 
$A$
 and 
$D$
 and a circle passing through the points 
$B$
 and 
$C$
 are externally tangent at a point 
$P$
 inside the quadrilateral. Suppose that 
\[\angle{PAB}+\angle{PDC}\leq  90^\circ\qquad\text{and}\qquad\angle{PBA}+\angle{PCD}\leq  90^\circ.\]
 Prove that 
$AB+CD \geq  BC+AD$.

\item[\textbf{G9.}]
Points 
$ A_{1}$, 
$ B_{1}$, 
$ C_{1}$
 are chosen on the sides 
$ BC$, 
$ CA$, 
$ AB$
 of a triangle 
$ ABC$
 respectively. The circumcircles of triangles 
$ AB_{1}C_{1}$, 
$ BC_{1}A_{1}$, 
$ CA_{1}B_{1}$
 intersect the circumcircle of triangle 
$ ABC$
 again at points 
$ A_{2}$, 
$ B_{2}$, 
$ C_{2}$
 respectively  
($ A_{2}\neq A, B_{2}\neq B, C_{2}\neq C$)
.  Points
$ A_{3}$, 
$ B_{3}$, 
$ C_{3}$
 are symmetric to 
$ A_{1}$, 
$ B_{1}$, 
$ C_{1}$
 with respect to the midpoints of the sides 
$ BC$, 
$ CA$, 
$ AB$
 respectively. Prove that the triangles 
$ A_{2}B_{2}C_{2}$
 and 
$ A_{3}B_{3}C_{3}$
 are similar.

\item[\textbf{G10.}]
Assign to each side 
$b$
 of a convex polygon 
$P$
 the maximum area of a triangle that has 
$b$
 as a side and is contained in 
$P$.
 Show that the sum of the areas assigned to the sides of 
$P$
 is at least twice the area of 
$P$.

