\item[\textbf{C1.}]
Let 
$ n > 1$
 be an integer. Find all sequences 
$ a_1, a_2, \ldots a_{n^2 + n}$
 satisfying the following conditions:
\[a_i \in \left\{0,1\right\} \text{ for all } 1 \leq i \leq n^2 + n \text{ and;}
\]
\[ a_{i + 1} + a_{i + 2} + \ldots + a_{i + n} < a_{i + n + 1} + a_{i + n + 2} + \ldots + a_{i + 2n} \text{ for all } 0 \leq i \leq n^2 - n.
\]

\item[\textbf{C2.}]
A rectangle 
$ D$
 is partitioned in several 
($ \ge2$)
 rectangles with sides parallel to those of 
$ D$.
 Given that any line parallel to one of the sides of 
$ D$, 
 and having common points with the interior of 
$ D$, 
 also has common interior points with the interior of at least one rectangle of the partition; prove that there is at least one rectangle of the partition having no common points with 
$ D$'s boundary.

\item[\textbf{C3.}]
Find all positive integers 
$ n$
 for which the numbers in the set 
$ S = \{1,2, \ldots,n \}$
 can be colored red and blue, with the following condition being satisfied: The set 
$ S \times S \times S$
 contains exactly 
$ 2007$
 ordered triples 
$ \left(x, y, z\right)$
 such that:
 
\begin{itemize}

\item[(i)]
 the numbers 
$ x$, 
$ y$, 
$ z$
 are of the same color,
and

\item[(ii)]
 the number 
$ x + y + z$
 is divisible by 
$ n$.

\end{itemize}

\item[\textbf{C4.}]
Let 
$ A_0 = (a_1,\dots,a_n)$
 be a finite sequence of real numbers. For each 
$ k\geq 0$, 
 from the sequence 
$ A_k = (x_1,\dots,x_k)$
 we construct a new sequence 
$ A_{k + 1}$
 in the following way.

\begin{itemize}

\item[1.] We choose a partition 
$ \{1,\dots,n\} = I\cup J$, 
 where 
$ I$
 and 
$ J$
 are two disjoint sets, such that the expression
\[ \left|\sum_{i\in I}x_i - \sum_{j\in J}x_j\right|
\]
attains the smallest value. (We allow 
$ I$
 or 
$ J$
 to be empty; in this case the corresponding sum is 0.) If there are several such partitions, one is chosen arbitrarily.


\item[2.] We set 
$ A_{k + 1} = (y_1,\dots,y_n)$
 where 
$ y_i = x_i + 1$
 if 
$ i\in I$, 
 and 
$ y_i = x_i - 1$
 if 
$ i\in J$.

\end{itemize}

Prove that for some 
$ k$, 
 the sequence 
$ A_k$
 contains an element 
$ x$
 such that 
$ |x|\geq\frac n2$.



\item[\textbf{C5.}]
In the Cartesian coordinate plane define the strips 
$ S_n = \{(x,y)|n\le x < n + 1\}$, 
$ n\in\mathbb{Z}$
 and color each strip black or white. Prove that any rectangle which is not a square can be placed in the plane so that its vertices have the same color.
 
\item[\textbf{C5'.}]

In the Cartesian coordinate plane define the strips 
$ S_n = \{(x,y)|n\le x < n + 1\}$
 for every integer 
$ n.$
 Assume each strip 
$ S_n$
 is colored either red or blue, and let 
$ a$
 and 
$ b$
 be two distinct positive integers. Prove that there exists a rectangle with side length 
$ a$
 and 
$ b$
 such that its vertices have the same color.

\item[\textbf{C6.}]
In a mathematical competition some competitors are friends. Friendship is always mutual. Call a group of competitors a 
clique
 if each two of them are friends. (In particular, any group of fewer than two competitiors is a clique.) The number of members of a clique is called its 
size.


Given that, in this competition, the largest size of a clique is even, prove that the competitors can be arranged into two rooms such that the largest size of a clique contained in one room is the same as the largest size of a clique contained in the other room.

\item[\textbf{C7.}]
Let 
$ \alpha < \frac {3 - \sqrt {5}}{2}$
 be a positive real number. Prove that there exist positive integers 
$ n$
 and 
$ p > \alpha \cdot 2^n$
 for which one can select 
$ 2 \cdot p$
 pairwise distinct subsets 
$ S_1, \ldots, S_p, T_1, \ldots, T_p$
 of the set 
$ \{1,2, \ldots, n\}$
 such that 
$ S_i \cap T_j \neq \emptyset$
 for all 
$ 1 \leq i,j \leq p$

\item[\textbf{C8.}]
Given is a convex polygon 
$ P$
 with 
$ n$
 vertices. Triangle whose vertices lie on vertices of 
$ P$
 is called 
good 
 if all its sides are equal in length. Prove that there are at most 
$ \frac {2n}{3}$
good
 triangles.

