\item[\textbf{A1.}]
Find all functions 
$f:\mathbb Z\rightarrow \mathbb Z$
 such that, for all integers 
$a,b,c$
 that satisfy 
$a+b+c=0$, 
 the following equality holds:
\[f(a)^2+f(b)^2+f(c)^2=2f(a)f(b)+2f(b)f(c)+2f(c)f(a).\]


(Here 
$\mathbb{Z}$
 denotes the set of integers.)

\item[\textbf{A2.}]
Let 
$\mathbb{Z}$
 and 
$\mathbb{Q}$
 be the sets of integers and rationals respectively.


(a) Does there exist a partition of 
$\mathbb{Z}$
 into three non-empty subsets 
$A,B,C$
 such that the sets 
$A+B, B+C, C+A$
 are disjoint?


(b) Does there exist a partition of 
$\mathbb{Q}$
 into three non-empty subsets 
$A,B,C$
 such that the sets 
$A+B, B+C, C+A$
 are disjoint?


Here 
$X+Y$
 denotes the set 
$\{ x+y : x \in X, y \in Y \}$, 
 for 
$X,Y \subseteq \mathbb{Z}$
 and  for 
$X,Y \subseteq \mathbb{Q}$.

\item[\textbf{A3.}]
Let 
$n\ge 3$
 be an integer, and let 
$a_2,a_3,\ldots ,a_n$
 be positive real numbers such that 
$a_{2}a_{3}\cdots a_{n}=1$.
 Prove that
\[(1 + a_2)^2 (1 + a_3)^3 \dotsm (1 + a_n)^n > n^n.\]

\item[\textbf{A4.}]
Let 
$f$
 and 
$g$
 be two nonzero polynomials with integer coefficients and 
$\deg f>\deg g$.
  Suppose that for infinitely many primes 
$p$
 the polynomial 
$pf+g$
 has a rational root. Prove that 
$f$
 has a rational root.

\item[\textbf{A5.}]
Find all functions 
$f:\mathbb{R} \rightarrow \mathbb{R}$
 that satisfy the conditions
\[f(1+xy)-f(x+y)=f(x)f(y) \quad \text{for all } x,y \in \mathbb{R},\]


and 
$f(-1) \neq 0$.

\item[\textbf{A6.}]
Let 
$f: \mathbb{N} \rightarrow \mathbb{N}$
 be a function, and let 
$f^m$
 be 
$f$
 applied 
$m$
 times. Suppose that for every 
$n \in \mathbb{N}$
 there exists a 
$k \in \mathbb{N}$
 such that 
$f^{2k}(n)=n+k$, 
 and let 
$k_n$
 be the smallest such 
$k$.
 Prove that the sequence 
$k_1,k_2,\ldots $
 is unbounded.

\item[\textbf{A7.}]
We say that a function 
$f:\mathbb{R}^k \rightarrow \mathbb{R}$
 is a metapolynomial if, for some positive integers 
$m$
 and 
$n$, 
 it can be represented in the form
\[f(x_1,\cdots , x_k )=\max_{i=1,\cdots , m} \min_{j=1,\cdots , n}P_{i,j}(x_1,\cdots , x_k),\]


where 
$P_{i,j}$
 are multivariate polynomials. Prove that the product of two metapolynomials is also a metapolynomial.

