
\item[\textbf{N1.}]
Let 
$\mathbb{Z} _{>0}$
 be the set of positive integers. Find all functions  
$f: \mathbb{Z} _{>0}\rightarrow \mathbb{Z} _{>0}$
 such that
\[ m^2 + f(n) \mid mf(m) +n \]


for all positive integers 
$m$
 and 
$n$.

\item[\textbf{N2.}]
Assume that 
$k$
 and 
$n$
 are two positive integers. Prove that there exist positive integers 
$m_1 , \dots , m_k$
 such that 
\[1+\frac{2^k-1}{n}=\left(1+\frac1{m_1}\right)\cdots \left(1+\frac1{m_k}\right).\]

\item[\textbf{N3.}]
Prove that there exist infinitely many positive integers 
$n$
 such that the largest prime divisor of 
$n^4 + n^2 + 1$
 is equal to the largest prime divisor of 
$(n+1)^4 + (n+1)^2 +1$.

\item[\textbf{N4.}]
Determine whether there exists an infinite sequence of nonzero digits 
$a_1 , a_2 , a_3 , \cdots $
 and a positive integer 
$N$
 such that for every integer 
$k > N$, 
 the number 
$\overline{a_k a_{k-1}\cdots a_1 }$
 is a perfect square.

\item[\textbf{N5.}]
Fix an integer 
$k>2$.
 Two players, called Ana and Banana, play the following game of numbers. Initially, some integer 
$n \ge k$
 gets written on the blackboard. Then they take moves in turn, with Ana beginning. A player making a move erases the number 
$m$
 just written on the blackboard and replaces it by some number 
$m'$
 with 
$k \le m' < m$
 that is coprime to 
$m$.
 The first player who cannot move anymore loses.


An integer 
$n \ge k $
 is called good if Banana has a winning strategy when the initial number is 
$n$, 
 and bad otherwise.


Consider two integers 
$n,n' \ge k$
 with the property that each prime number 
$p \le k$
 divides 
$n$
 if and only if it divides 
$n'$.
 Prove that either both 
$n$
 and 
$n'$
 are good or both are bad.

\item[\textbf{N6.}]
Determine all functions 
$f: \mathbb{Q} \rightarrow \mathbb{Z} $
 satisfying
\[ f \left( \frac{f(x)+a} {b}\right) = f \left( \frac{x+a}{b} \right) \]


for all  
$x \in \mathbb{Q}$, 
 
$a \in \mathbb{Z}$, 
 and 
$b \in \mathbb{Z}_{>0}$.
 (Here, 
$\mathbb{Z}_{>0}$
 denotes the set of positive integers.)

\item[\textbf{N7.}]
Let 
$\nu$
 be an irrational positive number, and let 
$m$
 be a positive integer. A pair of 
$(a,b)$
 of positive integers is called 
good
 if
\[a \left \lceil b\nu \right \rceil - b \left \lfloor a \nu \right \rfloor = m.\]
 A good pair 
$(a,b)$
 is called 
excellent
 if neither of the pair 
$(a-b,b)$
 and 
$(a,b-a)$
 is good.


Prove that the number of excellent pairs is equal to the sum of the positive divisors of 
$m$.